Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-05 apples_and_oranges.qmd
some more minor changes

Figure 1 graphs the results with the means of each level alongside their confidence intervals. Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metanalyses. 
As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms. Table 2 illustrates this with the output of one of the simulated models.

@@

```{r}
# examine the stability of the simulations

>>>>

Figure 1 graphs the results with the means of each level alongside their confidence intervals. Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metaregressions. 
As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms. Table 2 illustrates this with the output of one of the simulated models.

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# examine the stability of the simulations
